---
title: "1 - Description of Initially Available Data"
output: html_notebook
---

# Summary

A report of data quality necessary for planing of ETL activities for generation of a final and public repository of BRIGHTEN reserach data. Original files, their version, synapse ID, name, and contained variables are described in part 1. In part 2 all variables are described by the synapse ID of thier containing file, data type, frequency of subjects, frequency of tasks, mean, and standard deviation

# Environment

Python and the Synapse python library will need to be setup in the environment. Other variables and R libraries are fully configured here. Enter your username and password for Synapse.org.

```{r Setting Environment}
#Synapse login

REPOSITORY <- "syn5903785" #source synapse repo


#Needed Libraries 
# Setup loop to check in library is installed....
library(synapser) #Synapse API
library(reticulate) #Python integration into R studio
syn <- synLogin(USERNAME, PASSWORD)
synapseclient <- import('synapseclient')
synapseutils <- import('synapseutils') 
syn <- synapseclient$login(USERNAME, PASSWORD)

#library(PythonInR) #required to use some of sysapse API

#some libraries are used from python



#Constants

#File locations and directories
DATADIRECTORY <- "../Data/"

#variables

#HOMEDIR <- Sys.getenv("R_USER") #sets a constant for your home dir



```

# Extraction from Synapse

We will load the BRIGHTEN repository into the local Synapse cache.

```{r}
synapseutils$syncFromSynapse(syn, REPOSITORY)
  
  
  
synapseutils.syncFromSynapse(syn, entity=REPOSITORY)

```

The following files were chosen for review:



Data are extracted from the synology data repository. 

