---
title: "1 - Description of Initially Available Data"
output:
  html_document:
    df_print: paged
---

# Summary

A report of data quality necessary for planing of ETL activities for generation of a final and public repository of BRIGHTEN reserach data. Original files, their version, synapse ID, name, and contained variables are described in part 1. In part 2 all variables are described by the synapse ID of thier containing file, data type, frequency of subjects, frequency of tasks, mean, and standard deviation

# Environment

Python and the Synapse python library will need to be setup in the environment. Other variables and R libraries are fully configured here. Enter your username and password for Synapse.org.

```{r Setting Environment}
#Needed Libraries 
# Setup loop to check in library is installed....
#library(synapser) #Synapse API
library(knitr) #command line option in compiling notebook
library(tools)
library(xlsx) #read xmls files
library(data.table) 
library(reticulate) #Python integration into R studio
library(stringr) #parse strings


#library(PythonInR) #required to use some of sysapse API

#some libraries are used from python
synapseclient <- import('synapseclient')
synapseutils <- import('synapseutils') 

#Constants
#File locations and directories
DATADIRECTORY <- "../Data/"

SYNLOGIN <- synapseclient$login() #generate synology login token
```

# Loading Custom Functions

The following functions for working with our data are constructed and loaded here:

```{r loading custom functions}

#PRE string identifying volume label content, and synapse file description object (can be list)
#POST data frame describing the variables in each file named in the synapse object.
simple.content.listing <- function(VOL, INFO) {
  output <- data.frame(volume = character(),
                     synID = character(),
                     path = character(),
                     fileName = character(),
                     variables = character(),
                     stringsAsFactors = FALSE)
   `%!in%` <- Negate('%in%')
                    
  for(i in 1:(length(INFO))) {
    extension <- tools::file_ext(INFO[[i]]$files)
    if(extension == "tsv"| extension == "txt") {
      temp <-as.data.frame(fread(INFO[[i]]$path)) #read.table(INFO[[i]]$path, sep = "\t",  header = TRUE)
    }
    if(extension == "csv") {
      temp <- read.csv(INFO[[i]]$path, header = TRUE)
    }
    if(extension == "xls" | extension == "xlsx") {
      temp <- xlsx::read.xlsx(INFO[[i]]$path, sheetIndex = 1)
    }  
    if(!exists("temp")) {
      temp <- "file read error"
    }
    
    output[i,] <- c(VOL,
                    INFO[[i]]$properties$id,
                    INFO[[i]]$path,
                    INFO[[i]]$files,
                    paste(names(temp), collapse = ", "))
  }
   return(output)
}

custom.counter <- function(VOL, SID, DESC, USERS, DF) {
  #construct an empty dataframe meeting specifications
  toExport <- data.frame(volume = character(),
                         synID = character(),
                         description = character(),
                         userCount = numeric(),
                         uniqueObs = numeric())
  if(nrow(DF) > 0) {
    for (i in 1:ncol(DF)) {
      toExport[i,] <- c(VOL, 
                        SID,
                        DESC,
                        nrow(unique(DF[,USERS])),
                        sum(unique(DF)))
    }
  }
  return(toExport)
}

```

# Extraction from Synapse

```{r reading from repository}

#there is an error when trying to pull the full repository, and this error is repeated when trying to pull just the V1 directory and its subdirectories. More specicifcally, it appears that hte bulk data pull throws an error when encountering WIKI files, as is found in the analysis directory. Skipping this directory (putting from the other two directories under V1) bypasses this problem.

V1aInformation <- synapseutils$syncFromSynapse(SYNLOGIN, entity = "syn10236537", path = paste(DATADIRECTORY,"original/V1/", sep = "") )

V1bInformation <- synapseutils$syncFromSynapse(SYNLOGIN, entity = "syn5908558", path = paste(DATADIRECTORY,"original/V1/", sep = "") )

V2Information <- synapseutils$syncFromSynapse(SYNLOGIN, entity = "syn9952129", path = paste(DATADIRECTORY,"original/V2/", sep = "") )
```

The BRIGHTEN repository was loaded into a local project directory. This directory "../origina/." contains two subdirectories, one for each volume of data provided ("V1", "V2"). We ultimately want to create a single unified volume but need an accurate description of the data in order to build taat schema and data set.

# Building Proto-dictionaries

## Reporting files and their headers

```{r describing file columns}
FileContents <- simple.content.listing("V1", V1aInformation)
FileContents <- rbind(FileContents, simple.content.listing("V1", V1bInformation))
FileContents <- rbind(FileContents, simple.content.listing("V2", V2Information))
 
write.csv(FileContents[,!(names(FileContents) %in% "path")], paste("OriginalFileContents.csv", sep = ""))   

FileContents

```

## Reporting Matching of V1 and V2 Data

```{r}
MatchedRecords <- data.frame(V1SynID = character(),
                          V1FileName = character(),
                          V2SynID = character(),
                          V2FileName = character(),
                          stringsAsFactors = FALSE)

#PRE: a synID and or a file name of two different files to be matched
#POST: a list ocntaining both a synID and a file name for both files
add.match <- function(MasterList, V1SynID = NA, V2SynID = NA, V1FileName = NA, V2FileName = NA){
  if(is.na(V1SynID) & !is.na(V1FileName)) {
    V1SynID <- MasterList[MasterList$fileName == V1FileName,]$synID
  }
  if(is.na(V2SynID) & !is.na(V2FileName)) {
    V2SynID <- MasterList[MasterList$fileName == V2FileName,]$synID  
  }
  if(is.na(V1FileName) & !is.na(V1SynID)) {
    V1FileName <- MasterList[MasterList$synID == V1SynID,]$fileName
  }
  if(is.na(V2FileName) & !is.na(V2SynID)) {
    V2FileName <- MasterList[MasterList$synID == V2SynID,]$fileName
  }
  if(is.na(V1SynID) | is.na(V2SynID) | is.na(V1FileName) | is.na(V2FileName)) {
    print("error, unable to find all data")
    return()
  }
  return(c(V1SynID, V1FileName, V2SynID, V2FileName))
}


MatchedRecords[1,]<- add.match(FileContents, V1FileName =  "brighten_v1_passive_features.tsv", V2FileName = "passivedata_brighten_v2.tsv")

MatchedRecords[2,]<- add.match(FileContents, V1FileName =  "brighten_v1_phq2_scores.tsv", V2FileName = "phq2_brighten_v2.tsv")
MatchedRecords[3,]<- add.match(FileContents, V1FileName =  "brighten_v1_phq9_scores.tsv", V2FileName = "phq9_brighten_v2.tsv")
MatchedRecords[4,]<- add.match(FileContents, V1FileName =  "brighten_v1_study_metadata.tsv", V2FileName = "mdata_brighten_v2.tsv")
#MatchedRecords[5,]<- add.match(FileContents, V1FileName =  "005_allses_set.csv", V2FileName =                
#MatchedRecords[6,]<- add.match(FileContents, V1FileName =  "apps_399.xls", V2FileName =                     
#MatchedRecords[7,]<- add.match(FileContents, V1FileName =  "appsatisfaction_408.xls", V2FileName =           
MatchedRecords[8,]<- add.match(FileContents, V1FileName =  "energylevels_404.xls", V2FileName = "impact.csv")          
MatchedRecords[9,]<- add.match(FileContents, V1FileName =  "gad7_402.xls", V2FileName = "gad-7.csv")             
MatchedRecords[10,]<- add.match(FileContents, V1FileName =  "healthapps_405.xls", V2FileName = "health app overview.csv")             
MatchedRecords[11,]<- add.match(FileContents, V1FileName =  "mentalhealthservices_400.xls", V2FileName = "impact-mh.csv")   
MatchedRecords[12,]<- add.match(FileContents, V1FileName =  "moodassessment_407.xls", V2FileName = "pgic.csv")        
#MatchedRecords[13,]<- add.match(FileContents, V1FileName =  "qualityoflife_401.xls", V2FileName =             
MatchedRecords[14,]<- add.match(FileContents, V1FileName =  "sleep_406.xls", V2FileName = "sleep.csv")


#matches added as identified


```



## Reporting files and number of observations

```{r describing file volumes}

#indicating presence of possible key variables
FileInformation <- FileContents
FileInformation$user_id <- 0
FileInformation$brightenid <- 0
FileInformation$username <- 0
FileInformation$Response.ID <- 0

for(i in c(names(FileInformation)[5:8])) {
  for(j in 1:nrow(FileInformation)) {
    if(str_detect(FileInformation[j,"variables"], i)) {
      FileInformation[j,i] <- 1
    }
  }
}




FileInformation$uniqueObservations <- NA
FileInformation$uniqueObservations <- 



```



```{r}
#syn10236547 <- read.table(paste(V1a$cacheDir, "/",V1a$files, sep =""), header = TRUE)
#syn10236538 <- read.table(paste(V1b$cacheDir, "/",V1b$files, sep =""), header = TRUE)
```




